### 2020-08-11 thesis/thesis.tex
comment out dedication, update thesis format
move comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         Dedication                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetDedicationName{{Dedication}}%
\SetDedicationText{To be completed.}%
\Dedication%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         Acknowledgements                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetAcknowledgeName{{Acknowledgements}}%
% Among other acknowledgements, the student is required to declare the extent to which assistance (paid or unpaid) has been given by members of staff, fellow students, research assistants, technicians, or others in the collection of materials and data, the design and construction of apparatus, the performance of experiments, the analysis of data, and the preparation of the thesis (including editorial help).
% In addition, it is appropriate to recognize the supervision and advice given by the thesis supervisor(s) and advisors.
\SetAcknowledgeText{%
\noindent To be completed.
}%
\Acknowledge%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%       THESIS FORMAT AND STYLE       %% => UNSURE SO FAR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\SetLinkName{{Thesis Format}}%
%\SetLinkText{This thesis is written in a manuscript-based format.
%\\
%\\
%\textbf{Chapter 1:} Student, A. Supervisor, B. (2013), My First Chapter Title \textit{Journal of %Ecographic Informatics} 10 (1), 878887.
%\\
%\\
%}
%\Link%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        Contribution of Authors                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A doctoral thesis must clearly state the elements of the thesis that are considered original scholarship and distinct contributions to knowledge.
% Contributions of the student to each chapter must be explicitly stated.
% Contributions of any co-authors to each chapter must be explicitly stated.
\SetContribAuthorsName{{Contribution of Authors}}
\SetContribAuthorsText{\noindent
I am the first author for all chapters and the appendix in this
thesis.
\\
\\
\textbf{Chapter 1:} %TODO mention bronwyn for parts of the code, Guillaume and Bronwyn for parts of the code and for providing LANDIS summary for out model inputs. + Yanna and NRCAN.
I wrote the manuscript with input from my supervisor.
\\
\\
\textbf{Chapter 2:} %TODO mention NGOs, + Aurelie + Facilitators + Ministries
I wrote the manuscript with input from my supervisor.
\\
\\
}%
\ContribAuthors%
\listoffigures %
\listoftables %

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         Dedication                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \SetDedicationName{{Dedication}}%
% \SetDedicationText{}%
% \Dedication%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         Acknowledgements                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetAcknowledgeName{{Acknowledgements}}%

%TODO mention bronwyn for parts of the code, Guillaume and Bronwyn for parts of the code and for providing LANDIS summary for out model inputs. + Yann and NRCAN.

%TODO mention NGOs, + Aurelie + Facilitators + Ministries

% Among other acknowledgements, the student is required to declare the extent to which assistance (paid or unpaid) has been given by members of staff, fellow students, research assistants, technicians, or others in the collection of materials and data, the design and construction of apparatus, the performance of experiments, the analysis of data, and the preparation of the thesis (including editorial help).
% In addition, it is appropriate to recognize the supervision and advice given by the thesis supervisor(s) and advisors.

\SetAcknowledgeText{%
\noindent To be completed.
}%
\Acknowledge%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%       THESIS FORMAT AND STYLE       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetLinkName{{Thesis Format}}%
\SetLinkText{This thesis is written in a manuscript-based format.
\\
\\
\textbf{Chapter 1:} Lucet, V. Gonzalez, A. (2020), Integrating Land Use Change Modelling with Connectivity Modelling. %\textit{Journal of Ecographic Informatics} 10 (1), 878887.
\\
\\
\textbf{Chapter 2:} Lucet, V. Gonzalez, A. (2020), Integrating Stakeholders Perceptions of Connectivity Conservation Priorities into a Spatially Explicit Land Use and Connectivity Change Model. %\textit{Journal of Ecographic Informatics} 10 (1), 878887.
\\
\\
}
\Link%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        Contribution of Authors                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A doctoral thesis must clearly state the elements of the thesis that are considered original scholarship and distinct contributions to knowledge.
% Contributions of the student to each chapter must be explicitly stated.
% Contributions of any co-authors to each chapter must be explicitly stated.
\SetContribAuthorsName{{Contribution of Authors}}
\SetContribAuthorsText{\noindent
I am the first author for all chapters and the appendix in this
thesis.
\\
\\
\textbf{Chapter 1:} 
I wrote the manuscript with input from my supervisor.
\\
\\
\textbf{Chapter 2:}
I wrote the manuscript with input from my supervisor.
\\
\\
}%
\ContribAuthors%
\listoffigures %
\listoftables %
